### 2012-10-15 rebuttal.txt

Review 1:
- wrong track
- lack of description of the language
- too many implementation details
- metrics used
- research questions and conclusions

Review 2:
- Gigascope, point to the original NFQL paper

Review 3:
- Explain that NFQL is defined elsewhere, this paper is discussing
  implementation aspects.
- Discuss storage requirement vs. state requirement (after all NFQL
  is a streaming language but it requires state to be maintained)

Review 4:
- Explain what NFQL can do that other tools can't do
- Clarify the order splitter/filter in the query language and the
  order of filter/splitter in the implementation

### 2012-10-15 rebuttal.txt

Review 1:
1. wrong track
2. lack of description of the language
3. too many implementation details
4. metrics used
5. research questions and conclusions

Review 2:
1. Gigascope, point to the original NFQL paper

Review 3:
1. Explain that NFQL is defined elsewhere, this paper is discussing
   implementation aspects.
2. Discuss storage requirement vs. state requirement (after all NFQL
   is a streaming language but it requires state to be maintained)

Review 4:
1. Explain what NFQL can do that other tools can't do
2. Clarify the order splitter/filter in the query language and the
   order of filter/splitter in the implementation

JoSch's notes/comments
======================

Review 1
--------

Review 2
--------

Review 3
--------

Review 4
--------

1. The reviewer notes that the work is not state of the art. I think it is
mentioned a couple of times (even in the abstract) what flowy can do that
other's cant and in "related work" it is listed how it has even more abilities
than SiLK.

### 2012-10-16 rebuttal.txt

Review 1:
1. wrong track
2. lack of description of the language
3. too many implementation details
4. metrics used
5. research questions and conclusions

Review 2:
1. Gigascope, point to the original NFQL paper

Review 3:
1. Explain that NFQL is defined elsewhere, this paper is discussing
   implementation aspects.
2. Discuss storage requirement vs. state requirement (after all NFQL
   is a streaming language but it requires state to be maintained)

Review 4:

- can you explain why you need the splitter before the filtering blocks
and not the other way round? IMHO filtering should happen before
splitting (fig 1)

The the order of execution of the pipeline stages in the flow query
language [1] and in the NFQL implementation is different.  According to
the language specification, as briefly described in section III:

"The pipeline starts with the splitter. It takes the flow-records data
as input in flow-tools compatible format. The splitter is responsible to
duplicate the input data out to several branches without any processing
whatsoever. This allows each of the branches to receive an identical
copy of the flow data to process it independently."

However, we (and as did the reviewer) realized that in order to
efficiently process large traces, the NFQL implementation needs to sway
away from this design decision. As such, NFQL is implemented in a way to
give away the need for a splitter entirely, as described in section IV-B

"NFQL uses identifiers to reference a flow record in the char array.
This eliminated the need to copy all the flow-records when moving ahead
in the processing pipeline. As a result, there is no dedicated splitter
stage in the execution engine. Each branch references the flow records
from a common memory location. This helps keep the memory costs at a
minimum when multiple branches are involved."

As a result, there is no splitter in the NFQL implementation.

[1] V. Marinov and J. Schönwälder, “Design of a Stream-Based IP Flow
Record Query Language,” DSOM ’09.Berlin: Springer-Verlag, 2009, pp. 15–28

- can you explain why you do not filter flows on the fly?

We _do_ filter flows on the fly. This is described in section IV-B

"The execution engine, as defined by the flow query language must read
all the flow records of a supplied trace into memory before starting the
processing pipeline. Since, the filter stage uses the supplied set of
absolute rules to make a decision on whether or not to keep a flow
record; it has to pass through the whole in-memory recordset again to
produce the filter results. This technique involves multiple linear runs
on the trace and therefore slows down when the ratio of number of
filtered records to the total number of flow-records is high. We
optimized this behavior in NFQL by merging the filter stage with
in-memory read of the trace. This means, a decision on whether or not to
make room for a record in memory and eventually hold a pointer for it in
filter results is done upfront as soon as the record is read from the
trace. In addition, if a request to write the filter stage results to a
flow-tools file has been made, the writes are also made as soon the
filter stage decision is available, thereby allowing
reading-filtering-writing to happen in O(n) time, where n is the number
of records in the trace."

The previous prototype implementations (Flowy and Flowy 2.0) had this
issue. There was a separate filter stage and the flows were not filtered
on the fly. NFQL however _does_ filter flows on the fly. We even
evaluated the performance improvements of NFQL against Flowy 2.0 and saw
that NFQL now runs 10 times faster as shown in Fig 3.

- in IV.B you talk about indexes. What indexes have you used. Please cover
this topic better

Each flow record is stored as a char array. The trace is stored as an
array of these flow records. This allows NFQL to reference any flow
record using identifiers (indexes) in the array for O(1) retrieval.

- The work described on this paper is interesting but probably not the
state of the art in terms of performance and features (i.e. it's not a
step ahead but more a student project). Some examples are not easy to
understand.

We have tried to set forth the novelty of NFQL from the very outset,
The abstract for instance, clearly briefs out the functionality that
separates it from contemporary flow-processing tools:

"NFQL can process flow records, aggregate them into groups, apply
absolute or relative filters, invoke Allen interval algebra rules, and
merge group records."

In section II (related work), we reason how NFQL does more than the
surveyed contemporary flow-processing tools:

flow-tools and nfdump:
"The power of filtering rules in both the tools is however mostly
limited to absolute comparisons of flow attributes. As a result,
relative comparison amongst different flows or querying a timing
relationship among them is not possible." - which is possible in NFQL.
In fact, the capabilities of flow-tools and nfdump are just one of the
five stages of the NFQL's processing pipeline. They do not support
grouping, aggregation, merging et al.

SiLK: 
SiLK can group flows and merge group records. However, the parameters
over which grouping/merging can be done is faily limited:
"The grouping and merging operations can only be performed using
an equality operator. NFQL on the other hand, provides a much richer set
of comparisons operations, such as equal, not equal, greater than, less
than, greater or equal, less or equal."

"The newly formed groups, which are passed on to the group filter, can
also contain meta-information about the flow-records contained within
the group using the aggregate clause defined as part of the grouper
query. The possible aggregation operations are static, count, product,
sum, logical and/or/xor, arithmetic mean, standard deviation, union,
median, minimum and maximum." - whereas SiLK only supports sum and or
aggregation operations.

"The relative filtering on the groups are applied to express timing and
concurrency constraints using Allen interval algebra [6]." - The merger
can also match group records by putting timing characteristics under
considerations. No such Allen operations are possible in SiLK.

"The ungrouper is the final processing element of the pipeline. It
unwraps the tuples of group-records into individual flow-records,
ordered by their timestamps." - NFQL maintains flow membership information of
each group record. SiLK does not provide this feature. As a result, once
flows are grouped together in SiLK, there is no way to unfold the groups
to identify their member flows. As such, there is no ungrouper in SiLK.

In section V, we evaluate the performance of each tool against NFQL.
flow-tools and nfdump could only participate in one of the evaluations
due to their limited feature sets. In rest of the evaluations only SiLK
could participate. Even so, we had to carefully design queries to find a
common ground since most of the NFQL operations are not possible in SiLK.

We believe NFQL is major step ahead in this effort. Our first python
prototype Flowy was feature complete, but was extremely slow in
comparison to contemporary tools and therefore could not scale to
real-world traces.  NFQL is an efficient feature complete implementation
of our flow-query language. It is not just a reimplementation in C, but
the processing pipeline has been reimagined and optimized with crispier
data structures to allow it to scale to real-world traces. This makes
NFQL comparable to current flow-processing tools, in addition to
offering more feature-sets that are just not available elsewhere.

It is not clear from the review which examples are not easy to
understand, so it's hard to comment.

### 2012-10-16 rebuttal.txt

Review 1:
1. wrong track
2. lack of description of the language
3. too many implementation details
4. metrics used
5. research questions and conclusions

Review 2:
1. Gigascope, point to the original NFQL paper

Review 3:

- design advantages of the proposed tool are not explained, if this is
  because NFQL has already been proposed in another paper, then this
  work is derivative to a high degree
- again, because the proposed method (not tool) is not explained, and
  explanation of related tools lacks functional and methodological
  detail, it is difficult to judge WHY the proposed tool is better

The flow query language was introduced in [1]. It describes the _design_
advantages of the language. In fact, the expressiveness of the language
can be seen from [2] where we define queries to identify flow signatures
of popular applications. We have had a python prototype implementation
[3] in the past, however the prototype was extremely slow and could not
scale to real-world traces. This paper introduces NFQL, an efficient
implementation of the language. This is not just a reimplementation in
C, but the pipeline has been reimagined with crispier data structures to
allow the implementation to scale to real-world traces. This is the
first time we evaluate and show that NFQL is comparable to contemporary
flow-processing tools. This paper discusses these implementation aspects.

[1] V. Marinov and J. Schönwälder, “Design of a Stream-Based IP Flow
Record Query Language,” DSOM ’09
[2] V. Perelman, N. Melnikov, and J. Schönwälder, “Flow signatures of
Popular Applications,” IM '11.
[3] K. Kanev, N. Melnikov, and J. Schönwälder, “Implementation of a
stream-based IP flow record query language,” AIMS’10

- the method is a -QL -- a query language, which assumes fixed
  storage, while recent research on traffic processing moves away from
  the store-then-process approach

The query language of NFQL is _indeed_ stream-based. The processing
pipeline consists of a number of elements, which are connected with each
other via pipes. Each element gets a input _stream_, performs some sort
of operation on it and the output _stream_ is piped to the next element.
This only requires that NFQL maintains state information between the
elements. NFQL does not necessarily follow a store-then-process approach

@@

"The relative filtering on the groups are applied to express timing and
concurrency constraints using Allen interval algebra [6]." - The merger
can also match group records by putting timing characteristics under
considerations. No such Allen operations are possible in SiLK.

"The ungrouper is the final processing element of the pipeline. It
unwraps the tuples of group-records into individual flow-records,
ordered by their timestamps." - NFQL maintains flow membership information of
each group record. SiLK does not provide this feature. As a result, once
flows are grouped together in SiLK, there is no way to unfold the groups
to identify their member flows. As such, there is no ungrouper in SiLK.

In section V, we evaluate the performance of each tool against NFQL.
flow-tools and nfdump could only participate in one of the evaluations
due to their limited feature sets. In rest of the evaluations only SiLK
could participate. Even so, we had to carefully design queries to find a
common ground since most of the NFQL operations are not possible in SiLK.

We believe NFQL is major step ahead in this effort. Our first python
prototype Flowy was feature complete, but was extremely slow in
comparison to contemporary tools and therefore could not scale to
real-world traces.  NFQL is an efficient feature complete implementation
of our flow-query language. It is not just a reimplementation in C, but
the processing pipeline has been reimagined to allow it to scale to
real-world traces. This makes NFQL comparable to current flow-processing
tools, in addition to offering more feature-sets that are just not
available elsewhere.

### 2012-10-16 rebuttal.txt

[1] V. Marinov and J. Schönwälder, “Design of a Stream-Based IP Flow
Record Query Language,” DSOM ’09
[2] V. Perelman, N. Melnikov, and J. Schönwälder, “Flow signatures of
Popular Applications,” IM '11.
[3] K. Kanev, N. Melnikov, and J. Schönwälder, “Implementation of a
stream-based IP flow record query language,” AIMS’10

- the method is a -QL -- a query language, which assumes fixed
  storage, while recent research on traffic processing moves away from
  the store-then-process approach

The query language of NFQL is _indeed_ stream-based. The processing
pipeline consists of a number of elements, which are connected with each
other via pipes. Each element gets a input _stream_, performs some sort
of operation on it and the output _stream_ is piped to the next element.
This only requires that NFQL maintains state information between the
elements. NFQL does not necessarily follow a store-then-process approach

# i do not think this is what the reviewer understands as "stream-based"
# nfql is not able to process packages as they come. Because it allows
# to do relative comparison in the grouper and the merger, those stages
# need to have access to any record of the dataset
# an extension that could make nfql stream-based for the grouper is a
# shifting window which only evaluates a small neighbourhood of the
# packet that is currently evaluated
# but this idea fails for the merger
#  - josch

### 2012-10-16 rebuttal.txt

Review 1:
1. wrong track
2. lack of description of the language
3. too many implementation details
4. metrics used
5. research questions and conclusions

Review 2:

- great content, but it does not appear that this paper is a giant leap
  over prior work

We have had a python prototype implementation [1] in the past, however
the prototype was extremely slow and could not scale to real-world
traces. This paper introduces NFQL, an efficient implementation of the
language. This is not just a reimplementation in C, but the pipeline has
been reimagined with crispier data structures to allow the
implementation to scale to real-world traces. This is the first time we
evaluate and show that NFQL is comparable to contemporary
flow-processing tools. This paper discusses these implementation aspects.

[1] K. Kanev, N. Melnikov, and J. Schönwälder, “Implementation of a
stream-based IP flow record query language,” AIMS’10

- As such some of the older work is perhaps missing from the references.
  Comes to mind: "Gigascope: A stream database for network applications
  C Cranor, T Johnson, O Spataschek - SIGMOD03."

The reference to Gigascope is in our flow query language paper [1],
which is referenced in this paper.

[1] V. Marinov and J. Schönwälder, “Design of a Stream-Based IP Flow
Record Query Language,” DSOM ’09

### 2012-10-16 rebuttal.txt

Review 1:

- it has been submitted to the wrong track, as it focusses mostly on
  implementation aspects.

@juergen
can you please address this concern?

- " and merge group records." I guess it should be either 'merge' or 'group'.

The merger merges group-records. Group-records are a conglomeration of
multiple flows. The congolomeration takes place according to the query
given at runtime.

- What are your main conclusions?

* NFQL, an efficient feature-complete implementation of the flow query
  language that supersedes our original python prototype Flowy.
* NFQL, can now process real-world sized traces in matter of minutes,
  something which used to take days (or even weeks) in Flowy. This
  expands the scope of flow-processing tools given the added feature set
  capability offered by the language which is not available elsewhere.
* The performance evaluation reveal that NFQL is comparable to
  contemporary flow-processing tools. SiLK appears faster in some situations.
* The evaluation queries developed as a part of this research can
  incubate into a more general benchmark suite for flow query tools

- Why don't you describe the flow query language? Instead, you describe
  a processing pipeline. Neither does the paper contain any real
  description of the query language, nor does it show any example query.

The flow query language was introduced in [1]. It describes the language
in full detail. This paper discusses the implementation aspects of the
language. We briefly describe the processing pipeline because that
helps create a stand ground necessary to understand the tool. Our
previous usecase paper [2] defines a number of queries that use the language.

- Why do you always use the 'Output Flows/Input Flows' metric? Explain that.

The metric was used to blackbox each stage of the pipeline. This helped
isolate the stages to benchmarks them separately to identify areas that
may need attention.

- Where/what are the used queries?
  How can I reproduce/repeat your measurements?

The queries are in the git repository referenced as a footnote in the
paper. The JSON queries were omitted from the paper for brevity reasons

The measurements can be repeated by using the cites public trace
alongwith the queries in the repository. The benchmarking suite
developed as a part of the research will help automate the task.

### 2012-10-16 rebuttal.txt

Reviewer 1:
- main conclusions?

* NFQL, an efficient feature-complete implementation of the flow query
  language that supersedes our original python prototype Flowy [3].
* NFQL, can now process real-world sized traces in matter of minutes,
  something which used to take days (or even weeks) in Flowy. This
  expands the scope of flow-processing tools given the added feature set
  capability offered by the language which is not available elsewhere.
* The performance evaluation reveal that NFQL is comparable to
  contemporary flow-processing tools. SiLK appears faster in some situations.
* The evaluation queries developed as a part of this research can
  incubate into a more general benchmark suite for flow query tools

Reviewer 1, 3:
- flow query language description (design advantages)?
- example queries?

The flow query language was introduced in [1]. It describes the language
in full detail. This paper discusses the implementation aspects of the
language. We briefly describe the processing pipeline because that
helps create a stand ground necessary to understand the tool. Our
previous use-case paper [2] defines a number of queries that use the language.

Reviewer 1:
- 'Output Flows/Input Flows' metric?

The metric was used to blackbox each stage of the pipeline. This helped
benchmarks them separately to identify areas that may need attention.

Reviwer 1:
- used queries? reproduce/repeat your measurements?

The queries are in the git repository referenced as a footnote in the
paper. The JSON queries were omitted from the paper for brevity reasons
The measurements can be repeated by using the cited public trace
alongwith the queries in the repository. The benchmarking suite
developed as a part of the research will help automate the task.

Reviewer 4:
- filtering before splitting?

The filtering _does_ happen before splitting. In fact, NFQL is
implemented in a way to give away the need for a splitter entirely. As
such, there is no splitter in the NFQL implementation. This is described
in section IV-B: Splitter. This is one of the performance optimizations
that makes NFQL scale well with real-world traces.

Reviewer 4:
- filter flows on the fly?

We _do_ filter flows on the fly.
This is described in section IV-B: Filter

@@

The previous prototype implementations (Flowy and Flowy 2.0) had this
issue. There was a separate filter stage and the flows were not filtered
on the fly. NFQL however _does_ filter flows on the fly. We even
evaluated the performance improvements of NFQL against Flowy 2.0 and saw
that NFQL now runs 10 times faster as shown in Fig 3.

Reviewer 2:
- older references (gigascope)?

The reference to Gigascope is in our flow query language paper [1],

Reviewer 2, 4:
- not state of the art?
- not a giant leap over prior work?

We have had a python prototype implementation [3] in the past, however
the prototype was extremely slow. NFQL is not just a reimplementation in
C, but the pipeline has been reimagined with better data structures to
allow the implementation to scale to real-world traces. We show that
NFQL is comparable to contemporary flow-processing tools. This paper
discusses these implementation aspects.

The abstract briefs out the novelty and is elaborated in further
sections. For instance, In section II, we reason how NFQL does more:

flow-tools and nfdump:
The capabilities of flow-tools and nfdump are just one of the
five stages of the NFQL's processing pipeline. They do not support
grouping, aggregation, merging et al.

SiLK: 
* SiLK can group flows and merge group records. However, the parameters
over which grouping/merging can be done is faily limited:
* SiLK only supports sum and or aggregation operations compared to a huge
set of aggregation options available in NFQL.
* The NFQL merger can also match group records by putting timing
characteristics under considerations. No such Allen operations are
possible in SiLK.
* Once flows are grouped together in SiLK, there is no way to unfold the
groups to identify their member flows. As such, there is no ungrouper in SiLK.

[1] V. Marinov and J. Schönwälder, “Design of a Stream-Based IP Flow
Record Query Language,” DSOM ’09
[2] V. Perelman, N. Melnikov, and J. Schönwälder, “Flow signatures of
Popular Applications,” IM '11.
[3] K. Kanev, N. Melnikov, and J. Schönwälder, “Implementation of a
stream-based IP flow record query language,” AIMS’10

### 2012-10-16 rebuttal.txt

Reviewer 1:
- main conclusions?

* an efficient feature-complete implementation of the flow query
  language, supersedes our python prototype Flowy [3].
* can now process real-world sized traces in matter of minutes,
  something which used to take days in Flowy. This expands the scope of
  flow-processing tools, given the added feature set capability
  which is not available elsewhere.
* Performance evaluation reveal that NFQL is comparable to
  contemporary tools. SiLK appears faster in some situations.
* The evaluation queries developed can incubate into a more general 
  benchmark suite for flow query tools

@@

Reviewer 1:
- 'Output Flows/Input Flows' metric?

The metric was used to blackbox each stage of the pipeline. This helped
benchmarks them separately to identify areas that may need attention.

Reviwer 1:
- used queries? reproduce/repeat your measurements?

The queries are in the git repository referenced as a footnote in the
paper. The measurements can be repeated by using the cited public trace
alongwith the queries in the repository. The benchmarking suite
developed as a part of the research will help automate the task.

@@

Reviewer 4:
- filtering before splitting?

The filtering _does_ happen before splitting. In fact, NFQL is
implemented in a way to give away the need for a splitter entirely. As
such, there is no splitter in the NFQL implementation. This is described
in section IV-B: Splitter.

Reviewer 4:
- filter flows on the fly?

We _do_ filter flows on the fly. This is described in section IV-B:
Filter Flowy and Flowy 2.0 had this issue. There was a separate filter
stage and the flows were not filtered on the fly. NFQL however _does_
filter flows on the fly. We evaluated the performance improvements
against Flowy 2.0 and saw that NFQL now runs 10 times faster as 
shown in Fig 3.

@@

Reviewer 2:
- older references (gigascope)?

The reference to Gigascope is in our flow query language paper [1],

Reviewer 2, 4:
- not state of the art?
- not a giant leap over prior work?

NFQL is not just a reimplementation of Flowy in C, but the pipeline has
been reimagined with better data structures to allow NFQL to scale to
real-world traces. We show that NFQL is comparable to contemporary
flow-processing tools. This paper discusses these implementation aspects.

@@

The abstract briefs out the novelty and is elaborated in further
sections. For instance, In section II, we reason how NFQL does more:

flow-tools and nfdump:
The capabilities of flow-tools and nfdump are just one of the
five stages of the NFQL's processing pipeline. They do not support
grouping, aggregation, merging et al.

SiLK: 
* SiLK can group flows and merge group records. However, the parameters
over which grouping/merging can be done is faily limited:
* SiLK only supports sum and or aggregation operations compared to a huge
set of aggregation options available in NFQL.
* The NFQL merger can also match group records by putting timing
characteristics under considerations. No such Allen operations are
possible in SiLK.
* Once flows are grouped together in SiLK, there is no way to unfold the
groups to identify their member flows. As such, there is no ungrouper in SiLK.

[1] “Design of a Stream-Based IP Flow Record Query Language,” DSOM ’09
[2] “Flow signatures of Popular Applications,” IM '11.
[3] “Implementation of a stream-based IP flow record query language,” AIMS’10

### 2012-10-16 rebuttal.txt

Reviewer 1:
- main conclusions?

* an efficient feature-complete implementation, 
  supersedes our python prototype Flowy [3].
* can now process real-world sized traces in minutes,
  This expands the scope of flow-processing tools, given the added 
  feature set capability which is not available in other tools.
* Evaluations reveal that NFQL is comparable to
  contemporary tools. SiLK appears faster in some situations.
* Evaluation queries can incubate into a more general 
  benchmark suite for flow query tools

@@

Reviewer 1, 3:
- flow query language description (design advantages)?
- example queries?

The language is described in detail in [1]. This paper discusses the
implementation aspects. We briefly describe the pipeline to help create
a stand ground necessary to understand the tool. Our previous use-case
paper [2] defines a number of queries to identify application
flow-signatures.

@@

Reviewer 1:
- 'Output Flows/Input Flows' metric?

The metric was used to blackbox each stage of the pipeline. This helped
benchmark them separately to identify areas that may need attention.

@@

Reviwer 1:
- used queries? reproduce/repeat your measurements?

The queries are in the git repository referenced in a footnote in the
paper. The measurements can be repeated by using the cited public trace
alongwith the queries in the repository. The developed benchmarking suite
will help automate the task.

@@

Reviewer 4:
- filtering before splitting?

The filtering _does_ happen before splitting. In fact, NFQL is
implemented in a way to give away the need for a splitter entirely. As
such, there is no splitter in the NFQL. This is described in section
IV-B: Splitter.

Reviewer 4:
- filter flows on the fly?

We _do_ filter flows on the fly. This is described in section
IV-B:Filter. Flowy and Flowy 2.0 had this issue. There is no longer a
separate filter stage in NFQL. NFQL now runs 10 times faster against
Flowy 2.0 as shown in Fig 3.

@@

Reviewer 2:
- older references (gigascope)?

The reference to Gigascope is in our flow query language paper [1],

Reviewer 2, 4:
- not state of the art?
- not a giant leap over prior work?

NFQL is not just a reimplementation of Flowy in C, but the pipeline has
been reimagined with better data structures to allow NFQL to scale to
real-world traces. This makes NFQL comparable to current flow-processing
tools. This paper discusses these implementation aspects.

The novelty of NFQL is discussed in section II:

* flow-tools/nfdump features are just one of the 5 stages of the pipeline. 
* SiLK only supports grouping/merging on an equality operator
* SiLK only supports sum and or aggregation operations. 
* SiLK does not support Allen operations. 
* SiLK cannot unfold groups to identify their member flows.

### 2013-01-13 sections/design.tex
reduced the content to 7 pages

The flow query language consists of a number of independent stages that are
connected to one another to form a processing pipeline.  Each stage receives
the content from the previous, performs an operation and pushes the results to
the next stage as shown in Fig. \ref{fig:nfql-pipeline}. A complete
description of the semantics of each pipeline stage can be found in
\cite{vmarinov:2009}.

@@

The filter is the first processing stage of a branch in the pipeline.  It
performs \emph{absolute} filtering on the input flow-records data.  The
flow-records that pass the filtering criterion are forwarded to the grouper,
the rest of the flow-records are dropped. The filter compares separate fields
of a flow-record against either a constant value or a value on a different
field of the \emph{same} flow-record. The filter cannot \emph{relatively}
compare two different incoming flow-records.

The grouper performs aggregation of the input flow-records. A flow-record in
order to be a part of the group should satisfy at-least one clause. A
flow-record, although, can be a part of multiple clauses, it cannot be part of
multiple groups. The grouping terms can be either absolute or relative. The
newly formed groups, which are passed on to the group filter, can also contain
meta-information about the flow-records contained within the group using the
aggregate clause defined as part of the grouper query. The possible
aggregation operations are \emph{static, count, product, sum, logical
and/or/xor, arithmetic mean, standard deviation, union, median, minimum and
maximum}.

The group-filter is the last processing stage of a branch. It performs
\emph{absolute} filtering on group-records. The group-records
that pass the filtering criterion are forwarded to the merger, the rest of the
group-records are dropped. The group-filter compares separate fields (or
aggregated fields) of a group-record against either a constant value or a value
on a different field of the \emph{same} group-record. The group-filter cannot
\emph{relatively} compare two different incoming group-records.

@@

The ungrouper is the final processing element of the pipeline. It unwraps the
tuples of group-records into individual flow-records, ordered by their
timestamps. Any duplicate flow-records appearing from several group-records
are eliminated and are sent as output only once.

>>>>

The flow query language consists of a number of independent stages that are
connected to one another to form a processing pipeline as shown in Fig.
\ref{fig:nfql-pipeline}. A complete description of the semantics of each
pipeline stage can be found in \cite{vmarinov:2009}.

@@

The filter is the first processing stage of a branch in the pipeline.  It
performs \emph{absolute} filtering on the input flow-records data.  The
flow-records that pass the filtering criterion are forwarded to the grouper,
the rest of the flow-records are dropped. The filter compares separate fields
of a flow-record against either a constant value or a value on a different
field of the \emph{same} flow-record.

The grouper performs aggregation of the input flow-records. The grouping
terms can be either absolute or relative. The newly formed groups, which are
passed on to the group filter, can also contain meta-information about the
flow-records contained within the group using the aggregate clause defined as
part of the grouper query. The possible aggregation operations are
\emph{static, count, product, sum, logical and/or/xor, arithmetic mean,
standard deviation, union, median, minimum and maximum}.

The group-filter is the last processing stage of a branch. It performs
\emph{absolute} filtering on group-records. The group-records
that pass the filtering criterion are forwarded to the merger, the rest of the
group-records are dropped. The group-filter compares separate fields (or
aggregated fields) of a group-record against either a constant value or a value
on a different field of the \emph{same} group-record.

@@

The ungrouper is the final processing stage of the pipeline. It unwraps the
tuples of group-records into individual flow-records, ordered by their
timestamps. Any duplicate flow-records appearing from several group-records
are eliminated.
